Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1].}

### 2018-11-13 paper/paper.tex
Work on parallel a bit

\author{Ciaran McCreesh\orcidID{0000-0002-6106-4871}\and
Patrick Prosser\orcidID{0000-0003-4460-6912} \and
James Trimble\orcidID{0000-0001-7282-8745}}

\authorrunning{C. McCreesh et al.}

@@

Our experiments are performed on systems with dual Intel Xeon E5-2697A v4 CPUs and 512GBytes RAM,
running Ubuntu 17.04, using GCC 7.2.0 as the compiler. We use a deterministic pseudo-random number
generator for reproducibility.  We use the dataset introduced by \citet{Kotthoff et al.\
}{DBLP:conf/lion/KotthoffMS16} for evaluation. This dataset brings together a range of
randomly-generated and application instance families from earlier papers:

@@

In \cref{figure:old-vs-new} we show the effects of adding restarts and nogood recording to the
algorithm. With restarts and nogood recording, the random value-ordering heuristic comfortably beats
the degree strategy with simple backtracking search. In other words, although having a good
value-ordering heuristic is beneficial, introducing randomness into the search is better, if it is
done alongside a mechanism to avoid heavy commitment to any particular random choice.
\Cref{figure:old-vs-new} also shows that the biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored heuristic than it is to throw away the heuristic altogether.  Indeed, the
original algorithm can solve 1,983 satisfiable instances by 993.0 seconds, whilst the biased and
random restarting algorithms require only 9.2 seconds and 33.8 seconds respectively to solve the
same number.

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-random-goods.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-random.pdf}
    \caption{On the left, not using nogood recording introduces slowdowns, particularly on
    unsatisfiable instances. On the right, using a random value-ordering gives much worse
    performance on many satisfiable instances.}
    \label{figure:features}
\end{figure}

As we might expect, these properties do not hold if any of the combination of changes are disabled.
In the left-hand plot of \cref{figure:features}, we see large slowdowns on unsatisfiable instances
when using a random value ordering and restarts but without nogood recording, and on the right-hand
plot we see many more satisfiable instances above the $x-y$ diagonal when using the random
value-ordering heuristic as opposed to the degree-biased heuristic.

@@

>>>>

\author{Blair Archibald\orcidID{????-????-????-????}\and
Ciaran McCreesh\orcidID{0000-0002-6106-4871}\and
Patrick Prosser\orcidID{0000-0003-4460-6912} \and
James Trimble\orcidID{0000-0001-7282-8745}}

\authorrunning{B. Archibald et al.}

@@

Our experiments are performed on the EPCC Cirrus HPC facility, on systems with dual Intel Xeon
E5-2695 v4 CPUs and 256GBytes RAM, running Centos 7.3.1611. ?? C++ native threads, MPI. We use GCC
7.2.0 as the compiler. ?? Steady clock times. We use a deterministic pseudo-random number generator
for reproducibility.

We use the dataset introduced by \citet{Kotthoff et al.\ }{DBLP:conf/lion/KotthoffMS16} for
evaluation. This dataset brings together a range of randomly-generated and application instance
families from earlier papers:

@@

In \cref{figure:old-vs-new} we show the effects of adding restarts and nogood recording to the
algorithm. With restarts and nogood recording, the random value-ordering heuristic comfortably beats
the degree strategy with simple backtracking search. In other words, although having a good
value-ordering heuristic is beneficial, introducing randomness into the search is better, if it is
done alongside a mechanism to avoid heavy commitment to any particular random choice.
\Cref{figure:old-vs-new} also shows that the biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored heuristic than it is to throw away the heuristic altogether.  Indeed, the
original algorithm can solve ?? satisfiable instances by ?? seconds, whilst the biased and
random restarting algorithms require only ?? seconds and ?? seconds respectively to solve the
same number.

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-biased-goods.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-random.pdf}
    \caption{On the left, not using nogood recording introduces slowdowns, particularly on
    unsatisfiable instances. On the right, using a random value-ordering gives much worse
    performance on many satisfiable instances.}
    \label{figure:features}
\end{figure}

As we might expect, these properties do not hold if any of the combination of changes are disabled.
In the left-hand plot of \cref{figure:features}, we see large slowdowns on unsatisfiable instances
when disabling nogood recording, and on the right-hand plot we see many more satisfiable instances
above the $x-y$ diagonal when using the random value-ordering heuristic as opposed to the
degree-biased heuristic.

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-parallel.pdf}

    \caption{Parallel}\label{figure:parallel}
\end{figure}
